Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
Discussing Figs

The gamification technique employed in this work is based on a rewarding mechanism  
\cite{dubois2013understanding}. In general rewards  consist of a reputation system 
with score points, levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. In these case
a point is awarded for each PUT sent to the server. Levels are a long
term achievement, in this case the level depends on the score:
\[ \text{level}(\text{score};a,b)= 
    \begin{cases} 
      0,                                    &  \text{score}\leq a\\    
      2(\frac{\text{score}-a}{b-a})^{2},    &  a\leq \text{score}\leq \frac{a+b}{2}\\
      1-2(\frac{\text{score}-b}{b-a})^{2},  & \frac{a+b}{2} \leq \text{score}\leq b\\
      1,                                    & \text{score}\geq b 
   \end{cases}
\]
The function returns a normalized value that is multiplied by the maximum level 
in this case 100. The variables $a$=100 and $b$=7360 give the slope of the function as
seen in Figure~\ref{fig:s}. The function was set to give users a rapid increase of 
levels at the beginning.
\begin{figure*}[t]
    \centering
        \includegraphics[width=3in]{img/s.png}
    \caption{$S$ function used to assign the user's level.
    }
    \label{fig:s}
\end{figure*}

@@

\subsection{Problem}
In the browser, each page visiting the experiment loads an HTML Worker
that runs a local island of an evolutionary algorithm to solve a
multi-modal problem called {\em l-trap}, which has been used extensively 
as a benchmark for evolutionary algorithms \cite{fernandes2009using,nijssen2003analysis}. 
This function counts the number of bits in a sequence $l$ and assigns
the local maximum $a$ if it has got 0 bits and the global maximum $b$ if it has $l$
bits. As seen in Figure \ref{fig:trap} the fitness falls into a {\em trap} 
as the number of bits is increased, decreasing linearly until a change in slope 
is reached at point $z$, adding deceptive component for evolutionary algorithms. 
To increase the difficulty trap functions can be concatenated. 
In our case we have used $40$ concatenated traps. The trap function  defined as:   
\[ f(u)= 
    \begin{cases} 
      \frac{a}{z}(z-u) & \text{if } u\leq z\\
      \frac{b}{l-z} (u-z)& \text{otherwise} 
   \end{cases}
\]
\begin{figure*}[t]
    \centering
        \includegraphics[width=3in]{img/trap.png}
    \caption{Trap function.
    }
    \label{fig:trap}
\end{figure*}

@@

\subsection{Results}
\label{sec:results}
At the end of the experiment the resulting log file contained 933,513 contributions both 
registered users and anonymous volunteers. Registered users where responsible of around
90\% of the contributions. The JSON data recorded for each contribution is  presented 
in Table~\ref{tab:record}.  
\begin{table}
  \small
  \caption{ Log file record structure}
  \label{tab:record} 
  \centering
  \small
  \begin{tabular}{l  l}
    \hline\noalign{\smallskip}
    Attribute & Value \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
    fitness & fitness as an integer.  \\ \hline
    IP & IP address of the participant (later anonymized) .\\ \hline
    user & user-name or the string `anonymous'.  \\ \hline
    worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
    level &  level of user or the string `info' \\ \hline
    message & Only PUT messages were recorded in this experiment. \\ \hline
    timestamp & A time-stamp based on the Unix epoch\\ \hline
  \end{tabular}
\end{table}
Contributions are expressed as the number of HTTP PUT requests sent to the server, 
in Figure~\ref{fig:puts} a comparison between registered vs anonymous users is 
presented.

\begin{figure*}[t]
    \centering
    \subfigure  [Registered Users]
    {
        \includegraphics[width=4in]{img/puts_user.png}
    }
    \subfigure  []
    {
        \includegraphics[width=4in]{img/puts_ip.png}
    }

@@

\begin{figure*}[t]
    \centering
        \includegraphics[width=4in]{img/puts_box.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}

>>>>

The gamification technique employed in this work is based on a rewarding mechanism  
\cite{dubois2013understanding}. In general rewards  consist of a reputation system 
with score points, levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. In these case
a point is awarded for each PUT sent to the server. Levels are a long
term achievement, in this case the level depends on the score:
\[ \text{level}(\text{score};a,b)= 
    \begin{cases} 
      0,                                    &  \text{score}\leq a\\    
      2(\frac{\text{score}-a}{b-a})^{2},    &  a\leq \text{score}\leq \frac{a+b}{2}\\
      1-2(\frac{\text{score}-b}{b-a})^{2},  & \frac{a+b}{2} \leq \text{score}\leq b\\
      1,                                    & \text{score}\geq b 
   \end{cases}
\]
The function returns a normalized value that is multiplied by the maximum level 
in this case 100. The variables $a$=100 and $b$=7360 give the slope of the function as
seen in Figure~\ref{fig:s}. The function was set to give users a rapid increase of 
levels at the beginning.
\begin{figure*}[t]
    \centering
        \includegraphics[width=2.5in]{img/s.png}
    \caption{$S$ function used to assign the user's level.
    }
    \label{fig:s}
\end{figure*}

@@

\subsection{Problem}
In the browser, each page visiting the experiment loads an HTML Worker
that runs a local island of an evolutionary algorithm to solve a
multi-modal problem called {\em l-trap}, which has been used extensively 
as a benchmark for evolutionary algorithms \cite{fernandes2009using,nijssen2003analysis}. 
This function counts the number of bits in a sequence $l$ and assigns
the local maximum $a$ if it has got 0 bits and the global maximum $b$ if it has $l$
bits. As seen in Figure \ref{fig:trap} the fitness falls into a {\em trap} 
as the number of bits is increased, decreasing linearly until a change in slope 
is reached at point $z$, adding deceptive component for evolutionary algorithms. 
To increase the difficulty trap functions can be concatenated. 
In our case we have used $40$ concatenated traps. The trap function  defined as:   
\[ f(u)= 
    \begin{cases} 
      \frac{a}{z}(z-u) & \text{if } u\leq z\\
      \frac{b}{l-z} (u-z)& \text{otherwise} 
   \end{cases}
\]
\begin{figure*}[t]
    \centering
        \includegraphics[width=2.5in]{img/trap.png}
    \caption{Trap function.
    }
    \label{fig:trap}
\end{figure*}
\begin{table}
  \small
  \caption{ Log file record structure}
  \label{tab:record} 
  \centering
  \small
  \begin{tabular}{l  l}
    \hline\noalign{\smallskip}
    Attribute & Value \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    chromosome   & The individual sent to the server as a string of 160 bits.  \\ \hline
    fitness & fitness as an integer.  \\ \hline
    IP & IP address of the participant (later anonymized) .\\ \hline
    user & user-name or the string `anonymous'.  \\ \hline
    worker\_uuid & unique identifier of the HTTP Worker that sent the participation.   \\ \hline
    level &  level of user or the string `info' \\ \hline
    message & Only PUT messages were recorded in this experiment. \\ \hline
    timestamp & A time-stamp based on the Unix epoch\\ \hline
  \end{tabular}
\end{table}

@@

\subsection{Results}
\label{sec:results}
At the end of the experiment the resulting log file contained 933,513 contributions both 
registered users and anonymous volunteers. Registered users where responsible of around
90\% of the contributions. The JSON data recorded for each contribution is  presented 
in Table~\ref{tab:record}.

Contributions are expressed as the number of HTTP PUT requests sent to the server, 
in Figure~\ref{fig:puts} a comparison between registered vs anonymous users is 
presented. There where only 18 registered users, and the exact number of anonymous
is not known as we only recorded the IP of the request, also a registered users 
could sometimes be anonymous too, this could be because the first time they visit
the application they automatically begin to work as anonymous. Nevertheless,
there were 91 distinct IPs that had `anonymous' as the user. In the plot of
anonymous users, some of the last in the rank could in fact be registered users, 
momentarily participating as anonymous. Even if this is not considered, only 
about 16\% of users attending the call decided to participate as named users. 
There is a notable difference in the amount of participation between the two
groups, and also in the slope of the plot.

\begin{figure*}[t]
    \centering
    \subfigure  [Registered users]
    {
        \includegraphics[width=4in]{img/puts_user.png}
    }
    \subfigure  [Anonymous users]
    {
        \includegraphics[width=4in]{img/puts_ip.png}
    }

@@

\begin{figure*}[t]
    \centering
        \includegraphics[width=4in]{img/puts_box.png}
    \caption{ Box-plot of the number of requests sent by registered users and anonymous IPs.
     In the \emph{y} axis are number or PUTs in a logarithmic scale.
    }
    \label{fig:box}
\end{figure*}
